Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
non det input
moved the stability spec description to the appendix

%-------------------------------
\subsection{Stability of closed-loop systems}
\label{ssec:stability}
%-------------------------------

@@

A discrete-time system is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
the unity circle, {\it i.e.}, their absolute value are less than 
one~\cite{astrom1997computer}. For a closed-loop system as~\eqref{eq:closedloopss}, 
the characteristic polynomial $P(z)$ should be computed as follows:
\begin{equation}
P(z)= \det( z I_{n} - A_d + B_d K ),
\end{equation}
where $I_{n}$ is the n-th order identity matrix.

@@

The input sequence $u_{k}$ is non-deterministic with known bounds $u^{+}$ and $u^{-}$, 
such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.

@@

\newpage
\appendix
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{LTI system Transformations and Equivalencies} \label{sec:appendix}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++

>>>>

%-------------------------------
\subsection{Stability of closed-loop systems}
\label{sec:stability}
%-------------------------------

@@

A discrete-time system is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
the unity circle, {\it i.e.}, their absolute value are less than 
one~\cite{astrom1997computer}. In this paper, we express 
the stability specification $\phi_{stability}$ in terms of  
Jury's criterion \cite{fadali}. A detailed description of this 
specification can be found in the Appendix~\ref{sec:appendix-stability}.

@@

The input $u_{k}$%is non-deterministic with 
has known bounds $u^{+}$ and $u^{-}$, 
such that ${u^{-} \leq u_{k} \leq u^{+}},\forall k\geq 0$.

@@

\newpage
\appendix
%-------------------------------
\section{Stability of closed-loop systems}
\label{sec:appendix-stability}
%-------------------------------

A discrete-time system is asymptotically stable if and only if all the roots 
of the characteristic polynomial ({\it i.e.}, the eigenvalues) are inside of 
the unity circle, {\it i.e.}, their absolute value are less than 
one~\cite{astrom1997computer}. In this paper, we express 
the stability specification $\phi_{stability}$ in terms of  
Jury's criterion \cite{fadali}. A detailed description of this 
specification can be found in the Appendix~\ref{sec:appendix-stability}.

For a closed-loop system as~\eqref{eq:closedloopss}, 
the characteristic polynomial $P(z)$ should be computed as follows:
\begin{equation}
P(z)= \det( z I_{n} - A_d + B_d K ),
\end{equation}
where $I_{n}$ is the n-th order identity matrix.

%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\section{LTI system Transformations and Equivalencies} \label{sec:appendix}
%+++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
